A simplified Plackett-Luce likelihood function for rank orders

### 2024-02-28 inst/ejs-sample.tex
talk about Checo

\begin{equation}
\log\mathcal{L}_{r,n}(a)=\log(B-1)-B\frac{r+1}{n} 
+ K + \mathcal{O}\left(n^{-2}\right)
\end{equation}

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  Season ranking is based on a points
allocation system wherein competitors are awarded points based on race
finishing order; points accumulate additively.  The overall
competition winner is the competitor who accumulates the most points
after the final race.  However, as argued by Hankin~\cite{hankin2023},
the drivers' {\em ranks} are statistically sufficient for analysis of

The methods discussed above may be used to assess Bradley-Terry
strengths of Formula 1 racing drivers.  Let us consider 2018 season as
an example and first consider Lewis Hamilton.

Lewis Hamilton is a

>>>>

\begin{equation}\label{asymptotic}
\log\mathcal{L}_{r,n}(a)=\log(B-1)-B\frac{r+1}{n} 
+ K + \mathcal{O}\left(n^{-2}\right)
\end{equation}

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  Season ranking is based on a points
allocation system wherein competitors are awarded points based on race
finishing order; points accumulate additively.  The overall
competition winner is the competitor who accumulates the most points
after the final race.  However, as argued by
Hankin~\cite{hankin2023_formula1points}, the drivers' {\em ranks} are
statistically sufficient for analysis using Plackett-Luce approaches.
The methods discussed above may be used to assess Bradley-Terry
strengths of Formula 1 racing driver Sergio P\'{e}rez (``Checo'') over
his career from 2011 to 2023.  Checo's Formula 1 performance began
somewhat inauspiciously in 2011 as second driver for Sauber for whom
he finished no higher than P7, but his performance rose subsequently,
culminating in his achievement of a startling 20 podium finishes in
2022-3.  Noting that Checo raced against 73 distinct competitors [this
  rendering estimation of the other players' Plackett-Luce strengths
  effectively impossible], we nevertheless are in a position to
estimate his career-span Bradley-Terry strength and estimate it as

we consider the following inference
problem:

\begin{equation}
  b = b(t) = \frac{e^{\alpha + \beta t}}{1+e^{\alpha + \beta t}},\qquad\alpha,\beta\in\mathbb{R}
\end{equation}

(that is, a logistic regression of generalizeBradley-Terry strength
$b$ against time).

There seems to be no easy analytical solution to
this, although Equation~\ref{asymptotic} would give
\begin{equation}
  \label{asymptoticcheco}
  \log\mathcal{L}(B)=m\log(B-1) -B\left(\frac{r_1+1}{n_1}+\ldots+\frac{r_m+1}{n_m}\right)
\end{equation}

over the whole $m$ seasons, where $r_i$ is Checo's rank in race
